Overlay databank unlocks data-driven analyses of biomolecules for all

### 2023-10-10 CoverLetter4.tex

Please find enclosed our manuscript titled
{\it NMRlipids Databank makes data-driven analysis of biomembrane properties accessible for all}, which we would like to submit for your consideration to be published as a Resource in \textit{ Nature Structural \& Molecular Biology}.

@@

By providing rapid open access to simulation data and automaticly assessing their quality against experiments, the NMRlipids Databank holds immediate practical relevance for the broad basic research community studying membranes in life sciences --- ranging from molecular cell biology to biomedical applications such as lipid nanoparticles. Even more importantly, the programmable interface for flexible implementation of data-driven and machine learning applications will advance new biological applications of MD simulation data. We validate the practical relevance of the NMRlipids Databank on functional and mechanistic understanding of biological process 
%how molecular components in a work together
by successfully analysing how anisotropic diffusion of water and cholesterol flip-flop depend on membrane properties. Both of these processes are highly relevant for magnetic resonance imaging (MRI), pharmacokinetics, lipid trafficking, and regulating membrane properties of cellular membranes --- yet their timescales are beyond the scope of standard MD simulation investigations.

@@

We see that the NMRlipids Databank has both immediate and long term impact for a broad interdisciplinary audience of academic and industry researchers across life sciences: from biophysics and biochemistry to biology, biotechnology and biomedicine. Feedback on our first submission to \textit{Nature Methods} states that the manuscript is of interest on this field of research. Therefore, we trust our manuscript to fulfill the high standards for publication in \textit{ Nature Structural \& Molecular Biology}.
.\\

>>>>

Please find enclosed our manuscript titled
{\it Overlay databank unlocks data-driven analyses of biomolecules for all}, which we would like to submit for your consideration to be published as a Resource in \textit{ Nature Computational Science}.

@@

NMRlipids Databank is a groundbreaking tool that provides rapid open access to simulation data and automatic assessment of their quality against experiments. The programmable interface for flexible implementation of data-driven and machine learning applications will advance scientific research in wide range of fields
%new biological applications of MD simulation data. 
%, the  holds immediate practical relevance for the broad basic research community studying membranes in life sciences 
--- ranging from molecular cell biology to biomedical applications such as lipid nanoparticles. 
%Even more importantly, 
%We validate the practical relevance of the NMRlipids Databank on functional and mechanistic understanding of biological process 
%how molecular components in a work together
We demonstrate the power of NMRlipids databank to find novel insights and solve challenging real-world problems
by successfully analysing how anisotropic diffusion of water and cholesterol flip-flop depend on membrane properties. Both of these processes are highly relevant for magnetic resonance imaging (MRI), pharmacokinetics, lipid trafficking, and regulating membrane properties of cellular membranes --- yet their timescales are beyond the scope of standard MD simulation investigations.

%The journal publishes both fundamental and applied research, from groundbreaking algorithms, tools and frameworks that notably help to advance scientific research, to methodologies that use computing capabilities in novel ways to find new insights and solve challenging real-world problems.

@@

We see that the NMRlipids Databank has both immediate and long term impact for a broad interdisciplinary audience of academic and industry researchers across different disciplines: from biophysics and biochemistry to biology, biotechnology and biomedicine. Feedback from our first submissions to \textit{Nature Methods} and \textit{ Nature Structural \& Molecular Biology} states that the manuscript is of interest on these fields of research, yet the level of biological insight was not sufficient for these journals. Therefore, we believe that \textit{ Nature Computational Science} is the best forum for our manuscript and trust our manuscript to fulfill its high standards for publication. \\

### 2023-10-10 CoverLetter5.tex

Please find enclosed our manuscript titled
{\it Overlay databank unlocks data-driven analyses of biomolecules for all}, which we would like to submit for your consideration to be published as a Resource in \textit{ Nature Computational Science}.

@@

We see that the NMRlipids Databank has both immediate and long term impact for a broad interdisciplinary audience of academic and industry researchers across different disciplines: from biophysics and biochemistry to biology, biotechnology and biomedicine. Feedback from our first submissions to \textit{Nature Methods} and \textit{ Nature Structural \& Molecular Biology} states that the manuscript is of interest on these fields of research, yet the level of biological insight was not sufficient for these journals. Therefore, we believe that \textit{ Nature Computational Science} is the best forum for our manuscript and trust our manuscript to fulfill its high standards for publication. \\

>>>>

Please find enclosed our manuscript titled
{\it Overlay databank unlocks data-driven analyses of biomolecules for all}, which we would like to submit for your consideration to be published as a Resource in \textit{ Nature Communications}.

@@

We see that the NMRlipids Databank has both immediate and long term impact for a broad interdisciplinary audience of academic and industry researchers across different disciplines: from biophysics and biochemistry to biology, biotechnology and biomedicine. Feedback from our first submissions to \textit{Nature Methods}, \textit{Nature Structural \& Molecular Biology}, and \textit{Nature Computational Science} states that the manuscript is of significant interest on these fields of research, yet the level of biological insights or broader interest were not sufficient for these journals. Nevertheless, we believe that our manuscript represents important advances of significance to specialists within these fields, and therefore fulfills the high standards for a publication in \textit{ Nature Communications}. \\
